# Introduction {#intro}

```{block, type="tip"}
Here is a tip!
```

You can add sets of taxonomies. For example, I've created a test taxonomy of type `tags` with an entry labeled `tag`. Other uses of taxonomies include `projects`, or any other logical grouping of taxonomy sets. `projects` is included with a CSS style, but new taxonomy sets will need a new entry in the `taxonomies.css` file.

`r enterTaxonomy(name = "tag", reference = "intro", type = "tags", description = "")` 

It is important to add a separate output code chunk for each taxonomy type in the `9997-taxonomies.Rmd` file. Otherwise, the taxonomy set will not be included in the book.

Here is a `r enterGlossary(term = "Reference", definition = "This is a test reference.", reference = "intro", glossary = "main")`. There can be multiple entries for each glossary and separate glossaries can be created to group like terms. For example, a glossary may be useful for concept terms and another glossary for coding terms or functions. As with taxonomies, to include separate glossaries an output code chunk needs to be added. This will be in the `9998-glossary.Rmd` file. 

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
